Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-01-26 Journal1/paper2TNSM/pr.tex
add reviewr and bit change the pdf

One of the fifth-generation goals of the wireless cellular networks  is to achieve the desired QoS (such as rate, delay, power, ...) for different types of services. Network slicing is the best solution for this aim. 
Network slicing can support the heterogeneity of services by allocating different resources to each slice serving specific services to guarantee QoS, and isolating each service from the other services.
A network slice is an end-to-end logical network that offers services with specific needs.  
Multiple isolated network slices run, manage, and work independently on the same infrastructure. 
Several implementations of network slicing include core slicing, RAN slicing, and slicing of both sections. 

@@

eMBB requires a higher transmission data rate in comparison with 4G systems. Moreover, eMBB service satisfies the demands of high capacity and throughput coverage.
URLLC requires low latency  and high reliability. URLLC contains services such as autonomous vehicles, tactile internet, or remote surgery.
mMTC consists of a vast number of low power internet of things (IoT) devices transmitting small payloads to a typical receiver. In addition, mMTC UEs include sensors for sensing, metering, and monitoring devices 

@@

Recently, RAN virtualization receives significant attention from industry and academia since it has remarkable benefits that increase flexibility and reduce CAPEX and OPEX and allow operators to add new capabilities to the network more quickly. In addition to RAN virtualization, openness and RAN intelligence are two pillars that encourage the Open Radio Access Network (O-RAN) Alliance to establish O-RAN as the next generation of RAN systems. 
The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both. CRAN divides RAN into two parts, radio remote head (RRH) and baseband unit (BBU).  Several distributed RRHs can be connected to a centralized BBU,  called BBU-pool \cite{han2019research}. 
Unlike the previous generation of RAN that divides RAN into two parts, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU). 
O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node that includes higher PHY, MAC, and RLC.
In addition, the O-CU contains two parts, which are the O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected via open and well-defined interface $F_1$.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation,
RAN Intelligent Controller (RIC)- Near Real-Time and O-Cloud. 
One of the necessities of the new generation of wireless networks is its intelligence.
Based on the requirement of an intelligent wireless network, O-RAN offers machine learning techniques. The two logical nodes RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC- Near Real Time, implement the algorithms for network intelligence 
\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.

>>>>

To achieve a desired level of quality-of-service (quality, delay, power, etc.) for different services and isolate each service from the other services, network slicing is the best solution for 5G wireless cellular networks. Several implementations of network slicing include core slicing, RAN slicing, and slicing of both sections. 

@@

The eMBB service fulfills the demand for high capacity and throughput. The URLLC also offers autonomous vehicles, tactile internet, remote surgery services, and other services of high quality and low latency. mMTC is comprised of many low-power internet of things (IoT) devices that transmit small payloads to a typical receiver, including sensors for sensing, metering, and monitoring

@@

Openness and RAN intelligence are two pillars that encourage the Open Radio Access Network (O-RAN) Alliance to establish O-RAN as the next generation of RAN systems. The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both. RAN virtualization has remarkable benefits that increase flexibility, reduce CAPEX and OPEX, and allow operators to add new capabilities to the network more quickly. CRAN divides RAN into two parts: radio remote head (RRH) and baseband unit (BBU). Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}. Unlike CRAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).

O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node with higher PHY, MAC, and RLC.
In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud. 
Based on the requirement of an intelligent wireless network for the next generation of RAN systems, O-RAN offers machine learning techniques. The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC- Near Real-Time, implement the algorithms for network intelligence 
\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
